\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{emnlp2018}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{multirow}
\usepackage[inline]{enumitem}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{xspace}
\usepackage{bbm}
\usepackage{amsfonts}
\usepackage{amsmath}
%\usepackage[]{algorithm2e}
%\usepackage{algorithmic}
%\usepackage{algpseudocode} 
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\newcommand\mycommfont[1]{\footnotesize\ttfamily{#1}}
\SetCommentSty{mycommfont}


\usepackage{ifthen}
\newcolumntype{g}{>{\columncolor{black!5}}c}
\newcolumntype{f}{>{\columncolor{black!5}}r}
%\newcolumntype{f}{>{\columncolor{black!5}}r}
%\newcolumntype{v}{>{\columncolor{black!5}}r}
\newcolumntype{L}[1]{>{\columncolor{black!5}}m{#1}}

\aclfinalcopy % Uncomment this line for the final submission
\def\aclpaperid{2164} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\usepackage{verbatim,toappendix}
%\newenvironment{toappendix}{}{}{}
%\newcommand{\makeappendix}{}

\newcommand\BibTeX{B{\sc ib}\TeX}
\newcommand\confname{EMNLP 2018}
\newcommand\conforg{SIGDAT}

\newcommand{\hal}[1]{}%{\textcolor{blue!50!red!70!white}{\textbf{[[Hal: #1]]}}}
\newcommand{\kathy}[1]{}%{\textcolor{blue!70!red!50!white}{\textbf{[[Kathy: #1]]}}}
\newcommand{\hidey}[1]{}%{\textcolor{green}{\textbf{[[Hidey: #1]]}}}

\title{Content Selection in Deep Learning Models of Summarization}

\author{Chris Kedzie \and Kathleen McKeown\\
  Department of Computer Science \\
  Columbia University \\
  {\tt \{kedzie,kathy\}@cs.columbia.edu} \\\And
  Hal Daum\'e III  \\
  University of Maryland, College Park \\
  Microsoft Research, New York City \\
  {\tt hal@cs.umd.edu} \\}


\date{}

\begin{document}
\maketitle
\begin{abstract}
We carry out experiments with deep learning models of summarization across the domains of news, personal stories, meetings, and medical articles in order to understand how content selection is performed. We find that many sophisticated features of state of the art extractive summarizers do not improve performance over simpler models. These results suggest that it is easier to create a summarizer for  a new domain than previous work suggests and bring into question the benefit of deep learning models for summarization for those domains that do have massive datasets (i.e., news). At the same time, they suggest important questions for new research in summarization; namely,  new forms of sentence representations or external knowledge sources are needed that are better suited to the sumarization task. 
\end{abstract}

\input{macros}

\section{Introduction}
\input{introduction}

\section{Related Work} \label{sec:related}
\input{related_work}

\section{Methods}
\input{methods}

%\section{Models}
%\input{models}

\input{tables/table_data}
\input{tables/table_overall_results}
\section{Datasets}
\label{sec:datasets}
\input{datasets}
\input{tables/table_fixed_vs_learned}
\input{tables/table_pos_ablations.tex}
\input{tables/table_inorder_vs_shuffled.tex}


\section{Experiments} \label{sec:exps}
\input{experiments}

\begin{table*}[ht]
    \footnotesize
\centering
  \begin{tabular}{p{24em} p{24em}}
\toprule
Hurricane Gilbert swept toward the Dominican Republic Sunday, and the 
   Civil Defense alerted its heavily populated south coast to prepare 
   for high winds, heavy rains and high seas.                         
The storm was approaching from the southeast with sustained winds of  
   75 mph gusting to 92 mph.                                          
An estimated 100,000 people live in the province, including 70,000 in 
   the city of Barahona, about 125 miles west of Santo Domingo.       
\textbf{On Saturday, Hurricane Florence was downgraded to a tropical storm and
   its remnants pushed inland from the U.S. Gulf Coast.}               
Tropical Storm Gilbert formed in the eastern Caribbean and            
   strengthened into a hurricane Saturday night.  
&
Hurricane Gilbert swept toward the Dominican Republic Sunday, and the 
   Civil Defense alerted its heavily populated south coast to prepare 
   for high winds, heavy rains and high seas.                         
The storm was approaching from the southeast with sustained winds of  
   75 mph gusting to 92 mph.                                          
An estimated 100,000 people live in the province, including 70,000 in 
   the city of Barahona, about 125 miles west of Santo Domingo.       
Tropical Storm Gilbert formed in the eastern Caribbean and            
   strengthened into a hurricane Saturday night.                      
\textbf{Strong winds associated with the Gilbert brought coastal flooding,    
   strong southeast winds and up to 12 feet feet to Puerto Rico's     
   south coast.}   \\
\bottomrule
\end{tabular}
\caption{Example output of Seq2Seq extractor (left) and Cheng 
\& Lapata Extractor (right). This is a typical example, where only one
 sentence is different between the two (shown in bold). }
\label{tab:output}
\end{table*}

\subsection{Results} 
\input{results}



\section{Discussion}
\input{discussion}


\section{Conclusion}
We have presented an empirical study of deep learning based content selection
algorithms for summarization. Our findings suggest such models face stark limitations on their ability to learn robust features for this task and that 
more work is needed on sentence representation for summarization.


\section{Acknowledgements}
The authors would like to thank the anonymous reviewers for their valuable 
feedback. Thanks goes out as well to Chris Hidey for his helpful comments.

This research is based upon work supported in part by the Office of the 
Director of National Intelligence (ODNI), Intelligence Advanced Research 
Projects Activity (IARPA), via contract \# FA8650-17-C-9117. The views and 
conclusions contained herein are those of the authors and should not be 
interpreted as necessarily representing the official policies, either 
expressed or implied, of ODNI, IARPA, or the U.S. Government. The U.S. 
Government is authorized to reproduce and distribute reprints for governmental 
purposes notwithstanding any copyright annotation therein. 




\bibliography{emnlp2018}
\bibliographystyle{acl_natbib_nourl}

\newpage
\onecolumn
\appendix

\input{appendix}

\makeappendix

\end{document}
